OA Share

### 2021-01-27 analysis/006_license.Rmd
final results :-)

```{r}
license_by_year <- license_agg %>%
  mutate(license_code =
           case_when(
             grepl("/by/", license_url) ~ "CC-BY",
             grepl("/by-nc", license_url) ~ "CC-BY-NC-ND",
             grepl("userlicense", license_url) ~ "Els-User")
  ) %>%
  group_by(license_code, oa_type, issued_year) %>%
  summarise(n = sum(articles))
```
just immediate hybrid

@@

cc_hybrid <- im_hybrid %>%
  mutate(license_code = ifelse(grepl("/by/", URL), "CC-BY", "CC-BY-NC-ND")) %>%
  group_by(license_code, issued_year) %>%
  summarise(hybrid_immediate_articles = n()) %>%
  mutate(immediate = "immediate",
         oa_type = "Hybrid") %>%
  inner_join(license_by_year, by = c("issued_year", "license_code", "oa_type")) %>%
  mutate(hybrid_delayed_articles = n - hybrid_immediate_articles) %>%
  select(-immediate, -oa_type) %>%
  pivot_longer(c(hybrid_immediate_articles, hybrid_delayed_articles), names_to = "type", values_to = "articles")
# user only open archive
els_user <- license_by_year %>%
  filter(license_code == "Els-User") %>%
  mutate(type = "hybrid_delayed_articles") %>%
  group_by(issued_year, type, license_code) %>%
  summarise(articles = sum(n))
# full oa 
full_oa_df <- license_by_year %>%
  ungroup() %>%
  filter(license_code != "Els-User", oa_type == "Open Access") %>%
  mutate(type = "full_oa") %>%
  rename(articles = n) %>%
  select(-oa_type)
license_growth_df <- bind_rows(cc_hybrid, els_user, full_oa_df)

@@

```{r}
library(cowplot)
p_1 <- year_per_oa_type_and_license %>%
  mutate(type_plot = case_when(
    type == "full_oa" ~ "Full OA",
    type == "hybrid_immediate_articles" ~ "Hybrid OA",
    type == "hybrid_delayed_articles" ~ "Delayed OA"
  )) %>% 
  mutate(type_plot = factor(type_plot, levels = c("Hybrid OA", "Full OA", "Delayed OA"))) %>%
  ggplot(aes(gsub("20", "'", as.character(issued_year)), prop, fill = license_code, group = license_code)) +
  geom_area(stat = "identity",
            color = "white",
            alpha = 0.8,
            position = position_stack(reverse = T)) +
  facet_grid(~type_plot) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.0005)),
    labels = scales::percent_format(accuracy = 1L),
    breaks = c(0, 0.02, 0.04, 0.06, 0.08)
  ) +
  scale_fill_manual(values = 
                      c(`CC-BY` = "#B52141",
                        `CC-BY-NC-ND` = "#0093c7",
                        `Els-User` = "grey80")) +
  labs(x = "Publication Year", y = "OA Percentage") +
  theme_minimal_hgrid() +
  theme(legend.position = "top",
        legend.justification = "right") +
  guides(fill = guide_legend("Open Content License"))
p_1
```

>>>>

```{r}
license_by_year <- license_agg %>%
  mutate(license_code =
           case_when(
             grepl("/by/", license_url) ~ "CC BY",
             grepl("/by-nc", license_url) ~ "CC BY-NC-ND",
             grepl("userlicense", license_url) ~ "Els-User")
  ) %>%
  group_by(license_code, oa_type, issued_year) %>%
  summarise(n = sum(articles))
```
just immediate hybrid

@@

cc_hybrid <- im_hybrid %>%
  mutate(license_code = ifelse(grepl("/by/", URL), "CC BY", "CC BY-NC-ND")) %>%
  group_by(license_code, issued_year) %>%
  summarise(hybrid_immediate_articles = n()) %>%
  mutate(immediate = "immediate",
         oa_type = "Hybrid") %>%
  inner_join(license_by_year, by = c("issued_year", "license_code", "oa_type")) %>%
  mutate(hybrid_delayed_articles = n - hybrid_immediate_articles) %>%
  select(-immediate, -oa_type) %>%
  pivot_longer(c(hybrid_immediate_articles, hybrid_delayed_articles), names_to = "type", values_to = "articles")
# user only open archive
els_user <- license_by_year %>%
  filter(license_code == "Els-User") %>%
  mutate(type = "hybrid_delayed_articles") %>%
  group_by(issued_year, type, license_code) %>%
  summarise(articles = sum(n))
# full oa 
full_oa_df <- license_by_year %>%
  ungroup() %>%
  filter(license_code != "Els-User", oa_type == "Open Access") %>%
  mutate(type = "full_oa") %>%
  rename(articles = n) %>%
  select(-oa_type)
license_growth_df <- bind_rows(cc_hybrid, els_user, full_oa_df)

@@

```{r}
library(cowplot)
p_1 <- year_per_oa_type_and_license %>%
  mutate(type_plot = case_when(
    type == "full_oa" ~ "Full OA",
    type == "hybrid_immediate_articles" ~ "Hybrid OA",
    type == "hybrid_delayed_articles" ~ "Delayed OA"
  )) %>% 
  mutate(type_plot = factor(type_plot, levels = c("Hybrid OA", "Full OA", "Delayed OA"))) %>%
  ggplot(aes(gsub("20", "'", as.character(issued_year)), prop, fill = license_code, group = license_code)) +
  geom_area(stat = "identity",
            color = "white",
            alpha = 0.8,
            position = position_stack(reverse = T)) +
  facet_grid(~type_plot) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.0005)),
    labels = scales::percent_format(accuracy = 1L),
    breaks = c(0, 0.02, 0.04, 0.06, 0.08)
  ) +
  scale_fill_manual(values = 
                      c(`CC BY` = "#B52141",
                        `CC BY-NC-ND` = "#0093c7",
                        `Els-User` = "grey80")) +
  labs(x = "Publication Year", y = "OA Percentage") +
  theme_minimal_hgrid() +
  theme(legend.position = "top",
        legend.justification = "right") +
  guides(fill = guide_legend("Open Content License"))
p_1
```
